%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages

\usepackage{graphicx}
\usepackage{float}

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{BRSU} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Homework for Artificial Intelligence for Robotics\\Assignment 10 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Bastian Lang} % Your name

\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title


\section{Practical Part}

\subsection{Task}
Implement a simple \textit{Connect 4} game to demonstrate the use of adversarial search for
deterministic, fully observable, two player turn-taking zero-sum games.\\
For the adversarial search problem, implement a minmax and alpha-beta pruning agent
that allows you to play against the computer and/or the two algorithms against each other.
Compare these two approaches based on their search time, space requirement and other
information that you think is important. What was your evaluation function to rate the
board?

\subsection{Approach}
\subsubsection{Game}
In the beginning the user is asked to decide the two players. He has the opportunity to choose between a human player, the \textbf{MinMax} agent or the \textbf{Alpha-Beta-Pruning} agent.\\
My implementation uses a \textit{GameValidator} - class to check the current state of a board. This validator checks if the board is full and if in a single line, row or diagonal there are four connected stones of a kind.\\
The main part of the game runs in a while loop until the state has changed to either \textit{draw} or one of the two players won. In every cycle one of the two players is asked for his next move. The board gets checked afterwards and the current player changes.\\

\subsubsection{MinMax}
Because the search space is way too big to check it completely, I limited the depth of the search to 4 levels.\\
In the beginning I used an \textbf{evaluation function} that only checks terminal states, but with the depth limit and returning 0 if the limit is reached this will result in poor behaviour.\\
I thought about several strategies. One is to check the number of connected stones each row, diagonal and column and assign them a value depending on empty fields on both sides of the chain, on only one side or no empty fields left. But due to time issues and problems while implementing I instead went for a simpler solution.\\
In every row, diagonal and column I now check each possible set of neighbouring four stones. I evaluate each of those sets with respect to the number of missing stones to have four connected stones. I then compute the sum over all those sets and subtract the same for the opponents stones.

\subsection{Result}
I did not manage to implement the alpha-beta pruning agent, so I cannot compare both agents. But I expect the latter one to consume less space ;-)



\end{document}